Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-09 slides/slides.Rmd
updated slides

$$X = \begin{bmatrix}
\omega_1 \sqrt{\theta_{11}} & 0 \\ 
\vdots & \vdots \\ 
\omega_{n_1} \sqrt{\theta_{11}} & 0 \\ 
\omega_{n_1 + 1} \sqrt{\theta_{12}^2 / \theta_{11}} & \omega_{n_1 + 1} \sqrt{\theta_{22} - \theta_{12}^2 / \theta_{11}} \\ 
\vdots & \vdots \\
\omega_n \sqrt{\theta_{12}^2 / \theta_{11}} & \omega_n \sqrt{\theta_{22} - \theta_{12}^2 / \theta_{11}} \\ 
\end{bmatrix}$$

@@

ase.plot <- ggplot() + 
  geom_point(aes(x = Xhat[, 1],
                 y = Xhat[, 2],
                 colour = factor(z))) + 
  labs(x = NULL, y = NULL) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  scale_colour_brewer(palette = 'Set1')

>>>>

$$X = \begin{bmatrix}
\omega_1 \sqrt{p} & 0 \\ 
\vdots & \vdots \\ 
\omega_{n_1} \sqrt{p} & 0 \\ 
\omega_{n_1 + 1} \sqrt{r^2 / p} & \omega_{n_1 + 1} \sqrt{q - r^2 / p} \\ 
\vdots & \vdots \\
\omega_n \sqrt{r^2 / p} & \omega_n \sqrt{q - r^2 / p} \\ 
\end{bmatrix}$$

@@

ase.plot <- ggplot() + 
  geom_point(aes(x = Xhat[, 1],
                 y = Xhat[, 2],
                 colour = factor(z))) + 
  labs(x = NULL, y = NULL) + 
  theme_bw() + 
  theme(legend.position = 'none') + 
  coord_fixed() + 
  scale_colour_brewer(palette = 'Set1')
